---
title: gs_eda.R
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, echo=FALSE, tidy=TRUE, message=FALSE, warning=FALSE, dpi=300, fig.height=10.5, fig.width=10.5)
library(printr)
read_chunk("../../code/gs_eda.R")
```

##
##
## Growing season EDA [under development]

Here are some tentative plots and tables related to initial explorations of the thaw degree days (TDD) for the Growing Season project.

```{r setup2}
```

```{r plot_setup}
```

First, here is a map of the ecoregions currently in use.

```{r plot_eco, fig.height=7, fig.width=12}
```

### Marginal distributions

#### TDD by threshold and ecoregion

This plot shows propability density fucntions (pdfs) for TDD colored by percent TDD threshold and paneled by ecoregion.
These marginal densities integrate over space (map pixels) and time (years, 1982 - 2010).

```{r plot_marginal_tdd_01a}
```

#### 10% TDD by ecoregion and year

This plot shows the pdf specifically for the 10% TDD variable, by year and ecoregion.
These marginal densities integrate over space only.
Overlapping lines represent pdfs for individual years, 1982 - 2010.

```{r plot_marginal_tdd_01b}
```

The tables below provide aggregate information by TDD threshold and ecoregion.
Means and standard deviations are computed using all grid cells and all years for each combination of threshold and ecoregion.

```{r tables_tdd_mean_sd}
```
